### 2019-01-15 Sections/costs_and_attributes_in_quantum_networks.tex
just doing a save

From this, we can then define the \comment{accessible information}\index{Accessible information}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from which they would like to extract maximal correlations (i.e joint information). They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$ \comment{Changed from X,Y to A,B}. Their \comment{accessible information} is defined as,
\begin{align}
I_c(\hat\rho_{A,B}) = \max_{\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B).
\end{align}
\comment{Previously this was `classical mutual information'. Is that right? Isn't this actually the `accessible information'?}

@@

The \comment{\textit{classical channel capacity}}\index{Classical channel capacity} of quantum channel $\mathcal{E}$ is defined as,
\begin{align}
I(\mathcal{E}) = \max_{p(x)} I(X;Y),
\end{align}
\comment{What's p(x)?}
with the intuitive interpretation as the maximum mutual information between input and output states that can be achieved across the channel. This effectively places a physical upper bound on the achievable bitrate or bandwidth of the channel. For a noisy channel, if the input contains product states (i.e. entanglement between input states is not allowed), the classical channel capacity can be expressed as,
\begin{align}
\chi(\mathcal{E}) = \max_{p_i,\hat\rho_i} S(\hat\rho) - \sum_i p_i S(\hat\rho_i) \label{eq:holevoinfo}
\end{align}
\noindent which is known as the Holevo bound\index{Holevo bound}.

And the \textit{classical channel capacity} of $\mathcal{E}$ is defined as
\begin{align}\index{Classical!Channels!Capacity}
\mathcal{C}(\mathcal{E}) = \lim_{n \rightarrow \infty} \frac{I(\mathcal{E}^{\otimes n})}{n},
\end{align}
\comment{Added missing entropy/capacity measure in here that needs to act on E. Correct?}
which can be interpreted as the maximum bitrate of the channel, per use of the channel, in the limit of an infinite number of uses, where entangled between multiple applications is allowed in general.\comment{Why is this called the same thing as before but defined differently and using a different symbol for the metric?}

Analogous to the mutual information for classical systems is the \textit{coherent information} for quantum systems \cite{bib:PhysRevA.54.2629}, defined as,
\begin{align}\index{Coherent information}
I(\hat\rho,\mathcal{E}) = S(\mathcal{E}(\hat\rho)) - S_e(\hat\rho,\mathcal{E}).
\label{eq:mutual_info_classical_single}
\end{align}
Here $S_e$ is the \textit{exchange entropy}, a measure of how much information is exchanged between the state $\hat\rho$ and the environment under the action of the process. Specifically, it is given by the entropy of the environment subsystem in Eq.~(\ref{eq:proc_environment}), after application of the channel. This yields the intuitive interpretation that the coherent information is the information contained in the evolved state, discounted by the amount lost to the environment. It can be alternatively written as,
\begin{align}
I(A\>B) = H(B)_{\hat\rho} - H(A,B)_{\hat\rho},
\end{align}
\comment{The symbol $\backslash >$ doesn't work. Please correct this.}
which we recognise as the negative of the \textit{conditional quantum entropy}\index{Conditional quantum entropy},
\begin{align}
H(A|B) = H(A,B)_{\hat\rho} - H(B).
\end{align}
The fact that the information quantity $H(A|B)$ can be negative is a signature of the fundamental difference between the laws of classical and quantum information.

The quantum coherent information exhibits much of the same mathematical structure as the classical mutual information. And analogously
\begin{align}\index{Quantum channels!Capacity}
\mathcal{I}_Q(\mathcal{E}) = \max_{\hat\rho} I(\hat\rho,\mathcal{E}).
\label{eq:mutual_info_quantum_single}
\end{align}
\comment{What's this metric called? `quantum accessible information'?}

@@

\comment{One final request. Are you familiar with any analytic(!) results for channel capacities of Pauli channels, loss channels, or channels under the action of other simple/common error models? Would be handy to include these, if they are even known.}

>>>>

From this, we can then define the \textit{classical information of the channel}\index{c_i_c}, $I_c(\hat\rho_{A,B})$ -- the maximum of the mutual information, optimised over \textit{all} possible measurement settings. Suppose $\hat\rho_{A,B}$ is shared between Alice and Bob, from which they would like to extract maximal correlations (i.e joint information). They measure using local measurement bases $\{\Lambda_A^x\}$ and $\{\Lambda_B^x\}$, yielding random variables $A$ and $B$. Their \comment{classical information of the channel} is defined as,
\begin{align}
I_c(\hat\rho_{A,B}) = \max_{\{\Lambda_A^x\},\{\Lambda_B^x\}} I(A;B).
\end{align}
% \comment{Previously this was `classical mutual information'. Is that right? Isn't this actually the `accessible information'?}

@@

The \comment{\textit{classical mutual information}}\index{Classical channel capacity} of quantum channel $\mathcal{E}$ is defined as,
\begin{align}
I(\mathcal{E}) = \max_{p(x)} I(X;Y),
\end{align}
where the we optimize input state density $p(x)$.
The intuitive interpretation is that this is the maximum mutual information between input and output states that can be achieved across the channel. This effectively places a physical upper bound on the achievable bitrate or bandwidth of the channel. For a noisy channel, if the input contains product states (i.e. entanglement between input states is not allowed), the classical channel capacity can be expressed as,
\begin{align}
\chi(\mathcal{E}) = \max_{p_i,\hat\rho_i} S(\hat\rho) - \sum_i p_i S(\hat\rho_i) \label{eq:holevoinfo}
\end{align}
\noindent which is known as the Holevo bound\index{Holevo bound}.

And the \textit{classical channel capacity} of $\mathcal{E}$ is defined as
\begin{align}\index{Classical!Channels!Capacity}
\mathcal{C}(\mathcal{E}) = \lim_{n \rightarrow \infty} \frac{I(\mathcal{E}^{\otimes n})}{n},
\end{align}
% \comment{Added missing entropy/capacity measure in here that needs to act on E. Correct?}
which can be interpreted as the maximum bitrate of the channel, per use of the channel, in the limit of an infinite number of uses, where entangled between multiple applications is allowed in general.

Analogous to the mutual information for classical systems is the \textit{coherent information} for quantum systems \cite{bib:PhysRevA.54.2629}, defined as,
\begin{align}\index{Coherent information}
I(\hat\rho,\mathcal{E}) = S(\mathcal{E}(\hat\rho)) - S_e(\hat\rho,\mathcal{E}).
\label{eq:mutual_info_classical_single}
\end{align}
Here $S_e$ is the \textit{exchange entropy}, a measure of how much information is exchanged between the state $\hat\rho$ and the environment under the action of the process. Specifically, it is given by the entropy of the environment subsystem in Eq.~(\ref{eq:proc_environment}), after application of the channel. This yields the intuitive interpretation that the coherent information is the information contained in the evolved state, discounted by the amount lost to the environment. It can be alternatively written as,
\begin{align}
I(A\>B) = H(B)_{\hat\rho} - H(A,B)_{\hat\rho},
\end{align}

which we recognise as the negative of the \textit{conditional quantum entropy}\index{Conditional quantum entropy},
\begin{align}
H(A|B) = H(A,B)_{\hat\rho} - H(B).
\end{align}
The fact that the information quantity $H(A|B)$ can be negative is a signature of the fundamental difference between the laws of classical and quantum information.

The quantum coherent information exhibits much of the same mathematical structure as the classical mutual information. And analogously
\begin{align}\index{Quantum channels!Capacity}
\mathcal{I}_Q(\mathcal{E}) = \max_{\hat\rho} I(\hat\rho,\mathcal{E}).
\label{eq:mutual_info_quantum_single}
\end{align}
% \comment{What's this metric called? `quantum accessible information'?}

@@

% \comment{One final request. Are you familiar with any analytic(!) results for channel capacities of Pauli channels, loss channels, or channels under the action of other simple/common error models? Would be handy to include these, if they are even known.}
